% !TeX root = ../../main.tex
\documentclass[class=article, crop=false]{standalone}
\begin{document}

\section{Posets}
\label{sec:posets}

A partially ordered set or \emph{poset} $(P, \leq)$ is a set $P$ with a relation $\leq$ on pairs in $P$ which encodes the topology of $\R$. The textbook \cite{gratzer_lattice_2011} provides a good introduction. An important note is that there is no requirement for every pair to be related, hence the name \emph{partial order}. We will use $P$ as shorthand for $(P, \leq)$ where possible.

In a poset $P$ we define the \emph{interval} between two elements $[x,y]$ as $[x,y] \coloneq \Set{u \in P \given x\leq u \leq y}$, which is itself a poset. For convenience, we define $[-\infty,w] \coloneq \Set{u \in P \given u \leq w}$ and equivalently for $[w, \infty]$. A \emph{chain} is a subset $C \subseteq P$ that is a totally ordered, i.e.~every pair in $(u,v) \in C\times C$ satisfies $u\leq v$ or $v\leq u$. The \emph{covering relations} of $P$, denoted $\mathcal{E}(P)$ are defined as follows.
\begin{equation*}
	\mathcal{E}(P) = \Set{(x,y) \in P\times P \given x\leq y \,\, \text{and} \,\,  [x,y] = \Set{x,y}}
\end{equation*}

These are strictly ordered pairs $x < y$ such that there does not exist any $z \in P$ such that $x<z<y$. If $(x,y) \in \mathcal{E}(P)$, we write $x \lessdot y$. We will call a chain $C$ \emph{saturated} if for all $x,y \in C$ such that $x < y$, there exists $z \in C$ such that $x \lessdot z$, i.e.~there are no `gaps' in the chain.

By transitivity, the covering relations encode the whole poset structure, which can in turn be drawn in a diagram.

\begin{definition}
	Given a poset $P$, the \emph{Hasse Diagram} is the directed graph encoding $\mathcal{E}(P)$ in the following way: For each element $x \in P$ draw a vertex. For each pair $(x,y) \in \mathcal{E}(P)$ draw a directed edge from $x$ to $y$.
\end{definition}

As is typical, we will draw Hasse diagrams such that for each edge $x \lessdot y$, the vertex $x$ will be at a lower position on the page than $y$. Thus, we will not need to draw arrows to show direction. In this work, we will only with deal with graded and bounded posets. \emph{Bounded} means that there are minimal and maximal elements, denoted $\hat{0}$ and $\hat{1}$ such that $\hat{0} \leq x \leq \hat{1}$ for all $x \in P$, and \emph{graded} means that every saturated chain from $\hat{0}$ to $\hat{1}$ has the same (finite) length. In the Hasse diagram for a bounded, graded poset, we will draw $\hat{0}$ at the bottom, $\hat{1}$ at the top, and put all other elements in discrete vertical levels between these based on the position in the saturated chains between $\hat{0}$ and $\hat{1}$ where each element occurs. See \cref{fig:A4_interval} for an example. Graded posets have a natural notion of a \emph{rank function} $\rk \colon P \to \N$ that encodes the height above $\hat{0}$ at which an element $p \in P$ occurs in the Hasse diagram. Rank is also well--defined for posets with multiple minimal or maximal elements, so long as all saturated chains from any minimal element to any maximal element have the same length.

\begin{definition}
	We define an \emph{edge labelled poset} to be a triple $(P,\leq,l)$ where $(P,\leq)$ is a poset and the function $l: \mathcal{E}(P) \to A$ is a labelling of covering relations with alphabet $A$.
\end{definition}

% filled small circle
\tikzstyle{FSC}=[circle, draw=black!50,fill=black!20,thick, inner sep=0pt,minimum size=1.5mm]
\tikzstyle{a}=[red]
\tikzstyle{b}=[blue]
\tikzstyle{c}=[black!30!green]
\tikzstyle{light}=[black!22!white]

\begin{figure}
\centering
\begin{tikzpicture}
	\node[FSC] (base)		at (0,0)				[label=below:$\emptyset$]			{};
	\node[FSC] (bottom left)	at ($(base) + (-0.8,1) $)   		[label={[label distance=-0.1cm]200:$\{1\}$}]    {};
	\node[FSC] (bottom right)	at ($(bottom left) + (1.6,0)$)  	[label={[label distance=-0.1cm]300:$\{2\}$}]    {};
	\node[FSC] (top left)		at ($(bottom left) + (-1.1,1)$)    	[label=left:{$\{1,4\}$}]          		{};
	\node[FSC] (top middle)    	at ($(base) + (0,2)$)  			[label=right:{$\{1,3\}$}]			{};
	\node[FSC] (top right)    	at ($(bottom right) + (1.1,1)$)  	[label=right:{$\{2,3\}$}]          		{};
	\node[FSC] (top)          	at ($(base) + (0,3)$)    		[label=above:{$\{1,2,3,4\}$}]			{};
	
	\draw[a] (base) 		to 	node[auto] 		{a} 	(bottom left);
	\draw[b] (base) 		to 	node[auto, swap] 	{b} 	(bottom right);
	\draw[b] (bottom left)		to 	node[auto] 		{b} 	(top left);
	\draw[c] (bottom left)		to 	node[auto] 		{c} 	(top middle);
	\draw[a] (top middle)		to 	node[auto]		{a}	(top);
	\draw[a] (bottom right)		to 	node[auto, swap] 	{a} 	(top right);
	\draw[a] (top left)		to 	node[auto] 		{a} 	(top);
	\draw[b] (top right)		to 	node[auto, swap] 	{b} 	(top);
\end{tikzpicture}
\hspace{1cm}
\begin{tikzpicture}[baseline=-18pt]
	\node[FSC] (base)          	at (0,0)					{};
	\node[FSC] (bottom left)	at ($(base) + (-0.9,1) $)			{};
	\node[FSC] (bottom right)	at ($(bottom left) + (1.6,0)$)  		{};
	\node[FSC] (top left)		at ($(bottom left) + (-1.1,0.5)$)		{};
	\node[FSC] (top middle)    	at ($(base) + (-0.38,1.15)$)			{};
	\node[FSC] (top right)    	at ($(bottom right) + (1.1,0.5)$)		{};
	\node[FSC] (top)          	at ($(base) + (0,3)$)    			{};
	
	\draw (base) 			to					(bottom left);
	\draw (base) 			to 	  				(bottom right);
	\draw (bottom left)		to 	 				(top left);
	\draw (bottom left)		to 	 				(top middle);
	\draw (top middle) 		to 					(top);
	\draw (bottom right)	 	to 	  				(top right);
	\draw (top left) 		to 	 				(top);
	\draw (top right) 		to 	  				(top);
	
	
	\begin{pgfonlayer}{background}
		\draw[light] (base) 			to 	 				(top middle);
		\draw[light] (base) 			to 	  				(top);
		\draw[light] (base) 			to 	 				(top left);
		\draw[light] (base) 			to 	 				(top right);
		\draw[light] (bottom left) 	to 					(top);
		\draw[light] (bottom right) 	to 	  				(top);
	\end{pgfonlayer}
\end{tikzpicture}
\caption{A simple example of a bounded and graded edge labelled poset where we have taken $\leq$ to be $\subseteq$ and $A=\Set{a,b,c}$ (left). The same poset with all non-covering 1--chains drawn in faint lines to aid visualising $\Delta(P)$ introduced in \cref{sec:poset_cx} (right).}
\label{fig:example_edge_labelled_poset}
\end{figure}

We will use $P$ as a shorthand for $(P,\leq,l)$ where possible. Given an edge labelled poset $P$, we can construct a group encoded by its labelling the and geometry of its Hasse diagram.

The \emph{word corresponding to a saturated chain} is the word of the labels traversed in the Hasse diagram while tracing out that saturated chain.
\begin{definition}
	\label{def:poset_group}
	Given some edge labelled poset $(P,\,\leq,\,l \colon \mathcal{E}(P) \to A)$, define the \emph{poset group} $G(P)$ to be the group generated by $\image(l)$ with relations equating words corresponding to saturated chains in the Hasse diagram of $P$ which start and end at the same vertices.
\end{definition}

 In the example given in \cref{fig:example_edge_labelled_poset}, the poset group is $G(P) = \GroupPres{a,b,c \relations aba=bab,\, ba=ca}$.

\end{document}
